\documentclass[margin,line,pifont,palatino,courierm]{res}
\usepackage{pifont}
\usepackage{enumitem}
\usepackage[latin1] { inputenc}
\usepackage{hyperref}
\usepackage{color}
\usepackage{xcolor}
\topmargin -.5in
%\oddsidemargin -.5in
%\evensidemargin -.5in
%\textwidth=6.0in
 \textheight=9.0in
%\itemsep=0in
%\parsep=0in
\usepackage{fancyhdr}
%\topmargin=0in
%\textheight=8.5in
\pagestyle{fancy}
\renewcommand{\headrulewidth}{0pt}
\fancyhf{}
%\cfoot{\thepage}
%\lfoot{\textit{\footnotesize Research Statement}}
\rfoot{{\footnotesize Curriculum Vitae Louis de Thanhoffer de Volcsey}}
\definecolor{link}{RGB}{11, 0, 128}

\newenvironment{list1}{
  \begin{list}{\ding{113}}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in}
      \setlength{\leftmargin}{0.17in}}}{\end{list}}
\newenvironment{list2}{
  \begin{list}{$\bullet$}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in}
      \setlength{\leftmargin}{0.2in}}}{\end{list}}

\begin{document}

\name{Louis de Thanhoffer de Volcsey, Ph.D
\begin{description}
\vspace*{-0.2in}
\raggedleft
\item {\footnotesize \href{mailto:ldethanhoffer@me.com}{\color{link}\texttt{email}}
\vspace*{-.01in}
\item 
 \href{https://www.linkedin.com/in/louis-de-thanhoffer-de-volcsey-ph-d-243086135/}{\color{link}\texttt{linkedin }}
 \item 
 \href{http://www.louisdethanhoffer.com}{\color{link}\texttt{website}}
 \vspace{-.08in}
 \item 
 \texttt{(647)-983-8587 }
 }
\end{description}
}
\begin{resume}


\section{\sc Summary}

\begin{tabular}{| p{5in}}
Mathematical researcher with a passion for machine learning, looking to make a difference by combining a deep understanding of mathematical foundations together with a hands-on approach to the modeling challenges of tomorrow.\\	
\end{tabular}

\vspace{0.1in}
\section{\sc Skills}

\begin{tabular}{|  p{6in}}
Matlab, Python, TensorFlow, HTML/CSS, LaTeX.\\
English (fluent), French (native), Dutch (native), Hebrew (learning).\\

\end{tabular}
\vspace{0.1in}
\section{\sc Projects}
\begin{tabular}{|  p{5.1in}}
A ConvNet for image recognition\hfill  \hyperlink{}\href{https://github.com/ldethanhoffer/image_classification}{\hfill | \footnotesize \color{link} repository}\\
A classifier for discerning forgery in banknotes \hfill  \hyperlink{}\href{https://github.com/ldethanhoffer/banknote_forgery}{\hfill | \footnotesize \color{link} repository}\\\end{tabular}

\vspace{0.1in}
\section{\sc Experience}

{\bf Postdoctoral fellow} at University of Toronto, ON, CAN\hfill July 2015-present\\
\emph{Department of Computer and Mathematical Sciences}
\vspace{.1in}
\begin{list2}
\item Head instructor for  7 major courses ranging from cryptography to numerical linear algebra and advanced calculus.
\vspace{0.05in}
\item Author of a number of articles published in top tier journals.\hfill  \hyperlink{}\href{https://arxiv.org/find/math/1/au:+Volcsey_L/0/1/0/all/0/1}{\hfill | \footnotesize \color{link}  list}
\end{list2}

{\bf Program associate} at UC Berkeley, CA, US. \hfill  Spring 2013\\ 
\emph{Mathematical Sciences Research Institute}
\vspace{.1in}
\begin{list2}
\item Part of a handful of junior scientists globally selected to advance current research in algebra and geometry.
\end{list2}


{\bf Doctoral candidate} at University of Hasselt, BE\hfill Oct. 2009-June 2015\\
\emph{Faculty of Pure and Applied Mathematics}
\vspace{.1in}
\begin{list2}
\item Course instructor, senior thesis advisor and teaching assistant. 
\vspace{0.05in}
\item Invited speaker at AIM (Stanford, US.), IHP (Paris, Fr.), RIMS (Kyoto, JAP.), MFO (Oberwolfach, GER.), and Maxwell (Edinburgh, UK.).
\end{list2}



\section{\sc Education}


{\bf Certificate} in Machine Learning.\\\
\begin{list2}
\vspace*{-.1in}
\item \emph{Udacity} Machine learning engineering Nanodegree.\hfill{ August 2017}
\vspace{0.05in}
\item \emph{Coursera} Machine learning program. \hfill{Aug 2016}
\end{list2}


{\bf Ph.D.} in Pure Mathematics, University of Hasselt, BE.\hfill May 2015\\
\begin{list2}
\vspace*{-.1in}
\item \emph{Received honorable mention from the jury.}
\vspace{0.05in}
\item{Thesis in noncommutative geometry led to new developments in string theory.}
\end{list2}


{\bf M.Sc.} in Pure Mathematics, University of Antwerp, BE.\hfill May 2009\\
\begin{list2}
\vspace*{-.1in}
\item \emph{Summa cum laude.}
\end{list2}


{\bf B.Sc.} in Mathematics, Universtiy of Antwerp, BE.\hfill May 2007\\
\begin{list2}
\vspace*{-.1in}
\item \emph{Magna cum laude.}
\end{list2}
\newpage





\end{resume}
\end{document}
